Equation-of-state insensitive relations after GW170817

### 2019-04-09 paper/Response.txt

Dear Editor,

We would like to thank the referee for carefully reading our manuscript 
and providing valuable comments which have helped us improve the quality 
of our paper. For ease, we have highlighted all of our newest updates in 
boldface black. Additionally, we have outlined all of the comments
below, with "R:" and "A:" corresponding to the referee's comments and
the authors' replies, respectively.

We hope you reconsider publication of our manuscript in your journal.

Sincerely,

Zack Carson, Katerina Chatziioannou, Carl-Johan Haster, Kent Yagi, and 
Nicolás Yunes

---------------------------------------
Comments from the Referee
---------------------------------------

R: 1. I find the description of the “constrained” prior and its relation
to the “unconstrained” one slightly confusing. Sec. I A suggests that
it is constructed by sampling a large number of spectral EOSs and then
discarding those lying outside the 90% credible region of the EOS
posterior from GW170817. On the other hand, Sec. II A says that it is
built up from EOSs sampled directly from the EOS posterior (itself
derived from the unconstrained prior?), with no mention of the 90%
credible region. Naively, I would think that one would simply take the
unconstrained prior and reweight it by the GW170817 EOS likelihood to
get the constrained prior. Please explain more clearly which procedure
was adopted, and emphasize how the constrained and unconstrained
priors are related.

A: We apologize for the loss in translation between the descriptions of 
the constrained EoSs in the executive summary and Sec IIa. Ultimately, 
the "constrained" EoSs were computed identically to how the 90% 
posterior EoS were found in the paper by Abbott et al. So essentially we
are sampling the actual 90% posterior given by LIGO (the exact 
posterior EoSs from the paper are not publicly available, so the 
computation had to be re-done). Then, the unconstrained EoSs were 
generated completely randomly, with no relation to the constrained EoS
or the posterior PDF. We have modified our descriptions of this in both 
Sec. Ia and IIa.

R: 2. To quantify the error in the tidal deformability introduced by the
approximately universal nature of the binary Love relations, Sec. IV
adopts a representation for the error about the best-fit relation. The
error model is fitted to data from the constrained prior. Does this
prior include any hybrid EOSs, the models that deviate the most from
the binary Love relations? If not, do the projections in Sec. IV rely
on an implicit assumption that the EOS is purely hadronic?

A: Yes, you are correct that our results for the systematic errors from
the binary Love relations rely on the assumption of hadronic stars. Our 
set of constrained EoSs do not contain any hybrid star EoSs, following
from the calculations of Abbott et al on the EoS posterior probability 
distribution, which also assumed purely hadronic EoSs. If included these
results may change slightly, and could be a possible avenue of future
work. We have added a couple of sentences to the end of Sec. IVa 
noting this.

R:  3. Several papers have claimed that EOSs with sharp phase transitions
can violate I-Love-Q universality, e.g. Han & Steiner,
arXiv:1810.10967; Bandyopadhyay et al., Eur. Phys. J. A (2018) 54: 26;
Lau et al., Phys. Rev. D 95, 101302 (2017). Here, in Sec. III, hybrid
hadron-quark EOSs are found to obey the standard I-Love-Q relations.
Is this finding compatible with the existing claims in the literature?
The paper would benefit from a brief discussion of this point.

A: Upon reading over the papers by Han & Steiner, Bandyopadhyay et al, 
and Lau et al, we find that our results are indeed consistent with what
they present. 
The paper by Han & Steiner claims that "for typical neutron
stars > 1.0 M_sun, discrepancies are negligible", which can also be seen
in the bottom left panel of Fig. 11. In fact, the fits are only valid in
the M>1M_sun regime as can be seen in the top panel of Fig. 11, a relic 
fixed in our paper by using improved fits which limit to the Newtonian
case.
In the paper by Lau et al,  they claim that the "I-Love 
relation for hybrid stars still agrees with the universal relation for 
fluid stars to about 1% level for hybrid stars with a quark-matter core
surrounded by a fluid [hadronic] envelope", similar to what we investigate. 
They find that solid quark-matter stars (not studied by us) violate the 
relations proportionally to the value of the gap parameter. 
Finally, in the paper by Bandyopadhyay et al, there is no claim to *how* 
strongly the "HQ" EoSs violate the I-Love relation. However, by looking 
at Fig. we see that the departure from the "np" EoSs is not noticeably 
large, and seems to be somewhat consistent with what we see with our 
hybrid star EoSs. 
We also see in Paschalidis2018 (10.1103/physrevd.97.084038) that it was 
shown that the I-Love-Q universality is preserved for the hybrid stars
considered, which are identical to the ones used here.
As so, we have added a couple of sentences at the end of Sec.
IIIA2 discussing the consistency, as well as the additional references.

R:  4. In Fig. 5, the departure of the hybrid EOSs from the best-fit
binary Love relation appears to become more pronounced as q tends to
1. Is there an intuitive explanation for this behavior?

A: This behavior is caused for the same reason as the (fractional) error 
increases for hadronic stars with increasing mass ratio. This is because 
as the mass ratio decreases, the universal relation becomes more exact 
as Lambda_s -> Lambda_a (exactly equal in the q=0 limit). Therefore, as 
the mass ratio increases to 1, Lambda_a and Lambda_s become maximally 
different, and the fractional error becomes maximal. We have added a 
comment on this at the end of the caption on Fig. 5, as well as added 
the absolute differences for hybrid stars in the bottom three panels.

R:  * Sec. I: A more up-to-date reference about systematic errors in
neutron star mass-radius measurements is Miller & Lamb, F. Eur. Phys.
J. A (2016) 52: 63.

A: We thank the referee for the updated citation on M-R systematics. In 
response, we have added the Miller & Lamb 2016 citation in the first 
paragraph of Sec. I.

R: * Sec. I: The last sentence of the second paragraph seems to attribute
the tidal signature in the waveform solely to the modified orbital
dynamics, but there is an equally important dissipative contribution
due to the extra multipole radiation sourced by the tidal bulges.

A: We have modified the sentence in question to include this additional
GW modification effect: "These deformations source additional multipole radiation 
as well as affect the orbital trajectory of the binary, thus altering the
 GWs emitted, encoding within the latter the NS EoS."

R: * Sec. I A: Surely the variability in the R-Love relation is on the
order of hundreds of meters, not hundreds of kilometers.

A: We thank the referee for finding this typo! It is indeed errors of
~880 m and ~360 m, not km. This has been adjusted accordingly.

R: * Sec. II A: Why is causality only required to within 10% in the
prior? It does not appear to be explained in the text. (Also, Gamma is
incorrectly called the polytropic index instead of the adabiatic index
in this discussion.)

A: We chose causality to 10% to be consistent with the analysis of 
Abbott et al. 2018 (10.1103/PhysRevLett.121.161101), from which they 
choose to adhere to causality up to 10% upon deriving the EoS 
posterior probability distribution. We have added a short note to Sec. 
IIa. commenting on this. We have also fixed the incorrect naming of Gamma.

R: * Sec. IV: The sentence reporting the GW170817 Lambda_tilde
measurement does not cite the reference from which it was taken.
(Also, there appears to be an extraneous comment embedded in the same
sentence.)

A: We thank the referee for finding the missing citation and extraneous 
comment that somehow made it into the final draft. The citation has been
added, and comment removed.

---------------------------------------
Other Modifications
---------------------------------------

- We have included additional citations regarding the sentence 
"...but unfortunately, these [modified theories of gravity] are 
typically degenerate with the nuclear EoS. These are Pani & Berti 2014, 
Arxiv:1405.4547, Minamitsuji & Silva 2016, Arxviv:1604.07742, and 
Maselli & Silva 2016, Arxiv:1603.04876

### 2019-04-09 paper/Submit/bin-love-after-gw170817.tex
writing response to referee, as well as editing the paper

%Constraining the EoS
Independent measurements of NS observables can be used to constrain the nuclear EoS. For example, electromagnetic observations of the mass and radius of certain NSs have been used to place confidence limits in the mass-radius plane, and thus constrain the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}. These observations, however, may potentially suffer from large systematic errors~\cite{Miller2013} due to uncertainties in the astrophysical modeling of X-ray bursts. The gravitational waves (GWs) emitted in the coalescence of NS binaries may be a cleaner probe of nuclear physics. During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations determined by their nuclear EoS. These deformations affect the orbital trajectory of the binary, and thus the GWs emitted, encoding in the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.

@@

%How we improved this
We begin by investigating the increase in EoS insensitivity due to the constraints placed by GW170817 on the allowed space of EoSs. We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation. We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which this prior is enforced (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample). We repeat the analysis done by Yagi and Yunes~\cite{Yagi:binLove,Yagi:ILQ} on both sets of EoSs and find that the EoS-insensitive relations present less EoS variability with the constrained set. In particular, the EoS-insensitivity increases by a factor of $\sim 60$\% in the binary Love relations (for stars with mass ratio larger than $0.75$), by a factor of $\sim 70\%$ in the C-Love relations, and by factors of $\sim 50$\% in the I-Love-Q relations (see Table~\ref{tab:maxVar} and Fig.~\ref{fig:ILQ} for more details).

With this study at hand, we then carry out additional related studies on EoS-insensitive relations that go beyond the work in~\cite{Yagi:binLove,Yagi:ILQ}. First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, as these are critical in order to place constraints on the radius from a measurement of the Love number.  We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880 {\rm{km}}$ in the unconstrained case to $\sim 360 {\rm{km}}$ in the constrained case (see Sec.~\ref{sec:clove} for more details). Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018,Most:2018eaw,Burgio:2018yix,Montana:2018bkb}. We find that the I-Love-Q and C-Love relations remain EoS-insensitive for these hybrid stars, although the EoS variability increases slightly (see Sec.~\ref{sec:ilq-hyb} and~\ref{sec:clove-hyb} for more details). However, we also find that the binary Love relations are not EoS-insensitive for a mixed binary with a (massive) hybrid star and a (low-mass) hadronic star, due to the large separation in mass-weighted tidal deformability between the constituent stars (see Sec.~\ref{sec:binary} for more details).

@@

We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior. In \emph{both} cases, we model the EoS with a $C^{0}$-piecewise function that equals the low-density crust EoS of SLy~\cite{Douchin:2001sv} below half nuclear saturation density $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$~\cite{Read2009}, and equals the spectral decomposition described above outside the crust. For the latter, we restrict the spectral coefficients to the ranges $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and the adiabatic index is further restricted to $\Gamma \in \lbrack 0.6,4.5 \rbrack$~\cite{Lindblom:parameters}. Moreover, we impose the following two restrictions:  (i) causality within 10\%, i.e. that the speed of sound of the fluid be less than the speed of light to 10\%, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.

The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to a polytropic index $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction. 
To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}. We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to obtain samples from the EoS posterior. Our analysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}. 
In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.

@@

The fractional differences of hybrid stars from the fit for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases. The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:2013bca,Yagi:ILQ}, and is consistent with~\cite{Paschalidis2018}. The universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs. From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.

@@

\begin{figure}[htb]
\begin{center} 
\includegraphics[width=\columnwidth]{binLoveAbsolute.pdf}
\end{center}
\caption{(Color online) Binary Love relations using Eq.~\eqref{eq:binLovefit} fitted to the constrained (dotted maroon) and unconstrained sets (solid green), fixing $q=0.90$, 0.75 and 0.50. The bottom panels show the absolute difference (not the relative difference as in Fig.~\ref{fig:ILQ}) of the fit and the data. The fit to the constrained set shows a reduction in EoS variation relative to both the fit to the unconstrained set and previous work~\cite{Yagi:binLove}. For comparison, we also show the binary Love relations for the 10 hybrid star EoSs (dashed green curves), which present much larger EoS variation. 
}
\label{fig:binLove}
\end{figure}

@@

We have now shown that binary NS merger observations can help improve the EoS-insensitive relations, but the question remains: is it worth it?
Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
For example, GW170817 was detected by the second LIGO observing run (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva} Virgo is not formally an abbreviation,  so it's not all capitalized and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325 (or $\sigma_{\tilde{\Lambda}} \approx 198$).  This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
This implies that currently, the use of improved EoS-insensitive relations will only make a negligible difference on the extraction of tidal parameters.

@@

Figure~\ref{fig:qLsResiduals} shows the standard deviations of the $\lambda_0$ residuals binned in $q$ (top panel) and $\Lambda_{s}$ (bottom panel), as was done previously for the $\Lambda_a$ residuals. The EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2000$. Henceforth, in order to take into account these high-error regions of parameter space which may get averaged out, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval (rather than the $1\sigma$ uncertainty), which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}). We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.

>>>>

%Constraining the EoS
Independent measurements of NS observables can be used to constrain the nuclear EoS. For example, electromagnetic observations of the mass and radius of certain NSs have been used to place confidence limits in the mass-radius plane, and thus constrain the EoS~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}. These observations, however, may potentially suffer from large systematic errors~\cite{Miller:2016pom, Miller2013} due to uncertainties in the astrophysical modeling of X-ray bursts. The gravitational waves (GWs) emitted in the coalescence of NS binaries may be a cleaner probe of nuclear physics. During the early inspiral, the orbital separation is large enough that the tidal fields are negligible; but as the orbital separation decreases due to GW emission, tidal forces grow and the NSs respond by developing deformations determined by their nuclear EoS. 
These deformations \textbf{source additional multipole radiation as well as} affect the orbital trajectory of the binary, \textbf{thus altering} the GWs emitted, encoding \textbf{within} the latter the NS EoS~\cite{hinderer-love,Flanagan2008}.

@@

%How we improved this
We begin by investigating the increase in EoS insensitivity due to the constraints placed by GW170817 on the allowed space of EoSs. 
We take the 90\% credible region constructed from the posterior probability distributions on the pressure-density plane~\cite{Carney:2018sdv,LIGO:posterior} obtained from GW170817~\cite{TheLIGOScientific:2017qsa} as a prior on the set of EoSs that is compatible with this observation. 
We then generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, one in which \textbf{the EoSs are directly sampled from the posterior probability distribution} (the ``constrained'' sample) and another in which the prior is not enforced (the ``unconstrained'' sample). 
We repeat the analysis done by Yagi and Yunes~\cite{Yagi:binLove,Yagi:ILQ} on both sets of EoSs and find that the EoS-insensitive relations present less EoS variability with the constrained set. 
In particular, the EoS-insensitivity increases by a factor of $\sim 60$\% in the binary Love relations (for stars with mass ratio larger than $0.75$), by a factor of $\sim 70\%$ in the C-Love relations, and by factors of $\sim 50$\% in the I-Love-Q relations (see Table~\ref{tab:maxVar} and Fig.~\ref{fig:ILQ} for more details).

With this study at hand, we then carry out additional related studies on EoS-insensitive relations that go beyond the work in~\cite{Yagi:binLove,Yagi:ILQ}. First, we investigate the relation between the NS radius and its tidal deformability, the R-Love relations, for both sets of EoSs, as these are critical in order to place constraints on the radius from a measurement of the Love number.  We use the C-Love relations to construct the R-Love relations and find that the maximum EoS variability drops from $\sim 880$ \textbf{m} in the unconstrained case to $\sim 360$ \textbf{m} in the constrained case (see Sec.~\ref{sec:clove} for more details). Second, we study the EoS-universality of hybrid stars, which experience strong first-order phase transitions from hadronic to quark matter in the core~\cite{Paschalidis2018,Most:2018eaw,Burgio:2018yix,Montana:2018bkb}. We find that the I-Love-Q and C-Love relations remain EoS-insensitive for these hybrid stars, although the EoS variability increases slightly (see Sec.~\ref{sec:ilq-hyb} and~\ref{sec:clove-hyb} for more details). However, we also find that the binary Love relations are not EoS-insensitive for a mixed binary with a (massive) hybrid star and a (low-mass) hadronic star, due to the large separation in mass-weighted tidal deformability between the constituent stars (see Sec.~\ref{sec:binary} for more details).

@@

We here wish to consider EoS-insensitive relations using two sets of EoSs: a ``constrained set'' consistent with the observation of GW170817 and an ``unconstrained set'' that does not impose this prior. In \emph{both} cases, we model the EoS with a $C^{0}$-piecewise function that equals the low-density crust EoS of SLy~\cite{Douchin:2001sv} below half nuclear saturation density $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$~\cite{Read2009}, and equals the spectral decomposition described above outside the crust. For the latter, we restrict the spectral coefficients to the ranges $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_3 \in \lbrack -0.02,0.02 \rbrack$, and the adiabatic index is further restricted to $\Gamma \in \lbrack 0.6,4.5 \rbrack$~\cite{Lindblom:parameters}. Moreover, we impose the following two restrictions:  (i) causality within 10\%, i.e. that the speed of sound of the fluid be less than the speed of light to 10\% \textbf{(following the analysis of Ref.~\cite{LIGO:posterior})}, and (ii) a high maximum mass, i.e.~that the resulting EoS supports NSs with masses at least as high as $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations~\cite{1.97NS,2.01NS,Zhao:massiveNS}.

The unconstrained set is then defined by drawing random samples in the spectral coefficients within their allowed prior ranges, and then eliminating any EoS that either leads to \textbf{an adiabatic index} $\Gamma$ outside the allowed range, breaks the causality restriction, or breaks the maximum mass restriction. 
To obtain the constrained set of EoSs we analyze the publicly available data for GW170817 from the Gravitational Wave Open Science Center~\cite{GWOSC,Vallisneri:2014vxa}. 
We use the publicly available software library {\tt LALInference}~\cite{Veitch:2014wba,lalinference_o2} to \textbf{directly} obtain samples from the EoS \textbf{90\% posterior provided by Ref~\cite{LIGO:posterior}.}
Our analysis uses the same settings and prior choice as those of~\cite{LIGO:posterior,Carney:2018sdv}. 
In both cases, each set consists of 100 members, with a subset of these shown in the left panel of Fig.~\ref{fig:eos}.

@@

The fractional differences of hybrid stars from the fit for the second case (fit to only the constrained EoSs) is shown with dashed green lines in Fig.~\ref{fig:ILQ}, while the maximum EoS variation for the I-Love relation is shown in Table~\ref{tab:hybridCompare} for both the constrained and hybrid star cases. The hybrid star EoSs obey the I-Love-Q relations in each case to better than $\sim1.7$\%, a variability that is slightly higher than that found when using only nuclear matter EoSs in previous works~\cite{Yagi:2013bca,Yagi:ILQ}, and is consistent with~\cite{Paschalidis2018}. The universality cannot be improved much through the introduction of new fits, only bringing the maximal EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs. From this study, we conclude that hybrid star EoSs \emph{do} obey the traditional nuclear I-Love-Q relations computed with nuclear EoS data, albeit with a slight decrease in universality to $\sim1.7$\%.  
\textbf{We find this decrease in universality to be somewhat consistent with similar works~\cite{Paschalidis2018,Bandyopadhyay2018,PhysRevD.95.101302,Han:2018mtj}.
In such investigations, departures from universality of up to $\sim1\%-2\%$ were found with various hybrid star EoSs, compatible with our result of $\sim1.7$\%.}

@@

\begin{figure}[htb]
\begin{center} 
\includegraphics[width=\columnwidth]{binLoveAbsolute.pdf}
\end{center}
\caption{(Color online) Binary Love relations using Eq.~\eqref{eq:binLovefit} fitted to the constrained (dotted maroon) and unconstrained sets (solid green), fixing $q=0.90$, 0.75 and 0.50. The bottom panels show the absolute difference (not the relative difference as in Fig.~\ref{fig:ILQ}) of the fit and the data. The fit to the constrained set shows a reduction in EoS variation relative to both the fit to the unconstrained set and previous work~\cite{Yagi:binLove}. For comparison, we also show the binary Love relations for the 10 hybrid star EoSs (dashed green curves), which present much larger EoS variation.
Observe here how both hadronic and hybrid star EoSs alike seemingly observe increasingly small distinction from the fits as the mass ratio $q$ approaches 0.
While the absolute errors remain somewhat consistent with mass ratio, the fractional differences from the fit approach $0$ as $q\rightarrow0$ as the universal relation becomes exact ($\Lambda_s\rightarrow\Lambda_a$).
}
\label{fig:binLove}
\end{figure}

@@

We have now shown that binary NS merger observations can help improve the EoS-insensitive relations, but the question remains: is it worth it?
Current interferometer sensitivities are not yet high enough to accurately constrain the dominant tidal parameter $\tilde{\Lambda}$.
For example, GW170817 was detected by the second LIGO observing run (``O2")~\cite{aLIGO} and Virgo~\cite{TheVirgo:2014hva}, and was able to constrain $\tilde{\Lambda}$ to a $90\%$ credible interval centered at $\mu_{\tilde{\Lambda}}=395$ and with a width of 325~\cite{Abbott2018} (or $\sigma_{\tilde{\Lambda}} \approx 198$).  This corresponds to statistical uncertainties of ${\cal{O}}(80\%)$, which dominates the error budget compared to the small systematic uncertainties picked up by EoS variation in the EoS-insensitive relations.
This implies that currently, the use of improved EoS-insensitive relations will only make a negligible difference on the extraction of tidal parameters.

@@

Figure~\ref{fig:qLsResiduals} shows the standard deviations of the $\lambda_0$ residuals binned in $q$ (top panel) and $\Lambda_{s}$ (bottom panel), as was done previously for the $\Lambda_a$ residuals. The EoS-variability in $\lambda_0$ is dominated by the region around $q \sim 0.5$ and $\Lambda_{s} \sim 2000$. Henceforth, in order to take into account these high-error regions of parameter space which may get averaged out, we approximate the EoS-variability in the binary Love relations with the 90\% credible interval (rather than the $1\sigma$ uncertainty), which for the $\lambda_{0}$ parameter is $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}). We can similarly derive a conservative estimate of the systematic uncertainty due to EoS-variability in the binary Love relations in terms of $\tilde\Lambda_{a}$ to find $12.01$, which is what we use later in Fig.~\ref{fig:singleFisherLt}.
\textbf{Here we note that these results rely on the assumption of a purely hadronic EoS, as the constrained set of EoSs do not contain any hybrid stars.
This assumption was also made in Ref.~\cite{LIGO:posterior} upon the derivation of the posterior probability distribution.}
